Do More Polling Locations in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-05-30 outputs/paper/paper.qmd
Added data section and elections voting locations data sub-section and began formatting citations for both sections

>>>>

## Data
The data utilized throughout this paper was obtained through the City of Toronto’s OpenDataToronto Library [@rOpenDataToronto]. The two different data sets used are: “Elections Voting Locations” (Data, 2022) and “Elections - Voter Statistics” (Data, 2023). Data was collected and analyzed using the statistical programming software R (R Core Team, 2022), with additional support from from `tidyverse` [@rTidyverse], `ggplot2` [@rGgplot2], `dplyr` [@rDplyr], `readr` [@rReadr], `tibble` [@rTibble], and `janitor` [@rJanitor]. A further discussion of the data collection, cleaning, and analysis process can be found later on in this paper.

### Elections Voting Locations
This dataset, published by the City Clerk's Office [@VotingLocations] highlights all polling locations and subdivisions, on a ward-by-ward basis from the 2022 municipal election. This data was last refreshed on November 2, 2022 and captured for this paper on May 21, 2023. The polling locations account for Advance Vote, election day, and Mail In Voting. One subdivision in a ward is equivalent to one polling location, based on geography. In each ward, subdivision 97 accounts for Mail In Voting, while subdivisions 98 and 99 are designated Advance Vote locations. Voters can request a Mail In ballot, go to one of the two Advance Vote locations during the designated days, or vote at their assigned subdivision on election day (for example: ward 11, subdivision 11).
